\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
simulation setup finished

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Pre-compute Backup allocation for link failure on DC2$\to$DC4}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$.}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology. Each link has the same capacity 1Gbps but  different failure probability.}
\label{testbed}
\end{center}
\end{figure}

@@

We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 miniutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes and is repeated for 50 times, 
where link failures occur probabilistically,

@@

Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
Another factor we must pay attention into is the

@@

\begin{table}
\centering
\caption{Network topologies used in the simulations}\label{evaluation-topologies}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|} \hline
\setlength{\tabcolsep}{10pt}
\textbf{Topology Name}&\textbf{\#Nodes}&\textbf{\#Links}\\
\hline
IBM&18&48\\
\hline
B4&12&38\\
\hline
ATT&25&112\\
\hline
CERNET2&14&32\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Simulation evaluation}
\textbf{Simulation setup.} 
We evaluate the performance of $\mathsf{BATE}$ under four network topologies: B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE}, CERNET2 (China Education and Research Network), where the first three topologies (including their traffic metrics) are obtained from the authors of TEAVAR\cite{Teavar} and CERNET2 is measured by ourselves.
Table \ref{evaluation-topologies} shows the topology details.
To accommodate the reproducibility of link failures, we make the assumption that link failures fit Weibull distribution, which has been widely used in studying failures over backbones \cite{Characterization} and inter-DC WAN \cite{Teavar}.
Link failure probability varies each time slot with Weibull distribution.
Each run simulates 150000  1-minute timeslot (about 100 days).
The Weibull distribution probability density function $f(\lambda,k)$ contains two parameters, where $\lambda$ is shape parameter and $k$ is scale parameter.
We choose $f(0.8,0.00001)$ as our default distribution, which is similar to \cite{Teavar}.
Tenants' demands can arrive at anytime.
%After a request arriving the system, we run admitted control algorithm to determine whether the request can be accommodated or not.
%As introduced above, $\mathsf{BATE}$ adopts Algorithm \ref{greedy} as its default option.
%We compare Algorithm \ref{greedy} (i.e, Greedy) with fixed algorithm and the optimal algorithm
%The fixed algorithm assumes all admitted requests are fixed and checks whether the remaining network capacity can support the new request.
%The optimal algorithm determines whether the new request can be admitted by solving (\ref{P8}). 
%Every time slot, we randomly generate an integer $p$ between 0 and 10000 for each link.
%If  $p/10000$ is smaller than the failure probability of the link, we make it down to emulate failure.
%Then after 5 time slots, we make the link up again.
%Each experiment lasts 200 time slots.
%The achieved availability of a service is computed as the percentage of qualified time slots, where a slot is regarded as qualified if the total bandwidth is not smaller than demand.
%The achieved availability can be derived by a post-processing simulation composed by network states.
%In each network state, we record the application level throughput ratio as well as the network state probability.
%The sum of network state probability in which the allocated bandwidth larger than the demand is regarded as the achieved availability.
Traffic engineering performs every 10 time slots.
For traffic engineering part, we compare the performance of $\mathsf{BATE}$ against FFC \cite{FFC}, TEAVAR \cite{Teavar}, SWAN \cite{swan}, SMORE \cite{SMORE}, B4 \cite{B4}.
We change them to adapt service level traffic engineering: 
FFC tries to maximize the link utilization with considering 1 fault could occur in our evaluation.
%To fairly compare the ability of the FFC algorithm, we let it
%send the entire demand at the expense of potential degradation in
%availability, unless otherwise stated
%TEAVAR uses the parameter $\beta$ to control the network service availability target
TEAVAR maximizes bandwidth allocation to each demand subject to a single operator-specified availability target.
The default availability target of TEAVAR is $99.9\%$ in our simulations.
SMORE \cite{SMORE} minimizes the maximum link utilization without explicit guarantees on availability.
SWAN \cite{swan}  tries to  maximize the total throughput of all demands in the current slot.
B4 \cite{B4} aims to deliver max-min fair allocation manner to each demand.
%We compare the failure recovery part with random rerouting mechanism when there are link failures. 
%However, SWAN 
%However, TEAVAR .
%SWAN 
%We can see that DC5 takes about 100ms to detect failure and DC1 hears it within 200ms.
%It takes about 200ms for the controller to derive the new traffic engineering results.
%Switches take about 500ms to update flow rules.
%DC4-DC5 link has large failure probability, so the scenario mentioned above is likely to happen.
%Traditionally,  SDN controller will take reactive interventions when there are failures.
%This will take too much time and QoS might have already been hurt disastrously. 
%This demonstrates that $\mathsf{BATE}$ considers failure scenarios \textit{proactively}.
%Services with large availability target will pass links with low risk probability. 
%Therefore, the availability target can be guaranteed.
%$\mathsf{BATE}$ considers the failure probability of links, thus, the availability demand of applications can be guaranteed.
%\begin{figure*}
%\centering
%\subfigure[Network state coverage]{
%\includegraphics[width=0.32\textwidth]{fig/coverage.pdf}}
%\subfigure[Error]{
%\includegraphics[width=0.32\textwidth]{fig/error.pdf}}
%\subfigure[Solution time]{
%\includegraphics[width=0.32\textwidth]{fig/optimizer_times.pdf}}
%\caption{Impact of pruning and accuracy of solution.}
%\label{purning_fig2}
%\end{figure*}
%As introduced above, $\mathsf{BATE}$ calls for application level volume between each DC pair.
%Our collected traffic data contains the capacity of all links and the  bandwidth demands between each DC pair.
%We don't have real bandwidth demands of each service.
%%We assume there are $|J|=30$ application flows in each DC pair.
%To conform real data center network traffic characters, we divide the original DC-pair bandwidth demands into $|J|$ parts randomly, where the default value of $J$ is 30.
%%Each part can be regarded as an application flow demand.
%Services call for diverse availability demands and we generate them with uniform distribution between 90\% and 99.99\%.  
%There are typically five importance levels in current data centers, i.e., significant,
%important, normal, unimportant and lax.
%We randomly assign weights to services within \{1,2,3,4,5\}with uniform distribution, which is similar to \cite{hanzhang}.
% $\mu(f_{jtk})=\sum_{k\in K, t \in T_k}f_{jtk}/d_j, \forall j \in J$ in our experiments.
%Default  profit is 1 when availability is achieved, otherwise, the profit is $\mu(R_j)=0.01\times R_j$.
We consider 10 availability targets, which are chosen from the SLAs of Azure \cite{azure}.

\textbf{Workload.} 
%We perform trace-driven simulations.
Similar to previous work\cite{OWAN,Guaranteeings,Online-deadline,Teavar}, 
BA demands arrival time is also modeled as Poisson process with arrival rate $\lambda$ per time slot \cite{Guaranteeings,Online-deadline}.
The duration of each demand is modeled as an exponential distribution with a mean of 1000 time slots \cite{Guaranteeings}.
Our collected traffic data contains the capacity of all links as well as 200 bandwidth demands matrices for each topology.
To closely mimic the real traffic, bandwidth of each BA demand is randomly chosen from the real demands matrices, but each scales down 5 $\times$ \cite{Teavar}.

@@

\subsubsection{Performance under real network topologies}\label{scales}
%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{BATE}$.

>>>>

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Bandwidth allocation for DC2$\to$DC4 failure}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}

@@

\textbf{Evaluations on continuous demand arrivals.}
We first conduct experiments where user demands are generated from models used 
in some latest inter-DC traffic scheduling algorithms \cite{Guaranteeings,Online-deadline,OWAN,Teavar}. 
For each source-destination pair, the arrival of user bandwidth demands follows a poisson process, 
and the demand duration follows an exponential distribution.  
The mean inter-arrival time we use is 2 minutes, and the mean duration is 5 minutes. 
The demanded bandwidth is uniformly distributed between 10 Mbps and 50 Mbps.
The availability targets and refunding ratio are chosen from the Azure SLAs \cite{azure}, 
and we assume a unit price is charged for 1 Mbps. 
Each experiment lasts 100 minutes and is repeated for 50 times, 
where link failures occur probabilistically,

@@

\textbf{Evaluations on parallel demands.}
Now we use another example with three user demands to illustrate more details of $\mathsf{BATE}$. 
In our evaluation, we also compare with another scheme named BATE-TE, i.e, the traffic scheduling part of $\mathsf{BATE}$, with its fast failure recovery scheme abandoned. 
Demand-1 requires 1000Mbps from DC1 to DC3, demand-2 requires  500Mbps from DC1 to DC4, 
and demand-3 requires 1500Mbps from DC1 to DC5, 
with their availability target set as 99.5\%, 99.9\% and 95\%, respectively. 
We start their traffic simultaneously, assuming all of them have been admitted, 
and their bandwidth on each path, as shown in Table \ref{testbed-1}, 
is determined by different TE algorithms. 
The experiment lasts 100s and is repeated by 100 times.
Figure \ref{e1}(a) shows the fraction of time each bandwidth availability demand is satisfied, 
using the same method as in Figure \ref{e2}(a), i.e, for each second, 
a gap of more than 1\% bandwidth means the demand is not satisfied in that slot. 
It shows that all the three demands can reach their availability targets under $\mathsf{BATE}$,
while TEAVAR and FFC may fail for some users. 
With an investigation on the bandwidth allocation result in Table \ref{testbed-1}, 
we can see that, FFC reserves too much bandwidth for failure recovery, 
so that demand-1 never gets enough bandwidth (250 Mbps allocated v.s. 1500 Mbps demanded), 
and its achieved bandwidth availability is always 0. 
Even it allocates enough bandwidth for demand-2, the achieved bandwidth availability (98.2\%)  
is still lower than required (99.9\%). 
On the other hand, TEAVAR does not make a good match between the link failure probability and the availability users ask for. 
For example, for demand-2, which needs the highest level of availability (99.9\%), 
TEAVAR still allocates 250 Mbps on link L4, which has the highest failure probability (1\%) 
\footnote{In Figure \ref{e1}(b), we plot the actual number of failures that occur in the 100 experiments, 
where L4 fails most frequently.}. 
On the contrary, $\mathsf{BATE}$ matches demands and links well, and does not use L4 for user-2.
Another factor we must pay attention into is the

@@

\begin{table}
\centering
\caption{Network topologies used in the simulations}\label{evaluation-topologies}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|} \hline
\setlength{\tabcolsep}{10pt}
\textbf{Topology Name}&\textbf{\#Nodes}&\textbf{\#Links}\\
\hline
IBM&18&48\\
\hline
B4&12&38\\
\hline
ATT&25&112\\
\hline
a national-level backbone&14&32\\
\hline
\end{tabular}
\end{table}

@@

\subsection{Simulations}
\textbf{Simulation setup.} 
We also conduct simulations on four real network topologies, including B4 \cite{B4}, ATT \cite{Teavar}, IBM\cite{SMORE} and a national-level backbone. 
Table \ref{evaluation-topologies} shows the topology details
\footnote{For B4, ATT and IBM, we get their topologies, link capacities and traffic matrices from the authors of TEAVAR\cite{Teavar}, and for the national backbone, we conduct a direct measurement on it but hide its name due to anonymity requirement.}. 
Following the conclusion on WAN failures in literature studies\cite{Characterization, Teavar}, 
we simulate link failures according to a Weibull distribution with its shape $\lambda=0.8$ and scale $k=0.00001$. 
We generate the demand workload in a similar way to that in the testbed. 
The arrivals of BA demands follow a Poisson process, with a mean inter-arrival time of 2 minutes. 
The duration of each demand follows an exponential distribution, and the mean duration corresponds to 1000 time slots.
The required bandwidth in each user demand is randomly drawn from the traffic metrices (we have collected 200 matrices for each topology) with a proper scale down factor (we use 5), so that between each source-destination pair, multiple users can be served simultaneously. 
The required availability in each user demand is drawn from 10 different SLAs of Azure\cite{azure}.
In addition to FFC and TEAVAR, the TE algorithms we compare in simulations also include 
SWAN \cite{swan}, SMORE \cite{SMORE} and B4 \cite{B4}. 
We assume at most one link failure (i.e., no concurrent failures) in FFC,  
use 99.9\% (the maximum value in the user demands) as the default availability target in TEAVAR,
and let SWAN maximize the total throughput of all users. 
These TE algorithms will be activated every 10 time slots.
With the above settings, each simulation lasts 150,000 slots (corresponding to 100 days if each slot represents 1 minute), and the results that achieved by each algorithm on each topology are calculated on 5 independent simulations with different workload traces.

\iffalse
\textbf{Workload.} 
%We perform trace-driven simulations.
Similar to previous work\cite{OWAN,Guaranteeings,Online-deadline,Teavar}, 
BA demands arrival time is also modeled as Poisson process with arrival rate $\lambda$ per time slot \cite{Guaranteeings,Online-deadline}.
The duration of each demand is modeled as an exponential distribution with a mean of 1000 time slots \cite{Guaranteeings}.
Our collected traffic data contains the capacity of all links as well as 200 bandwidth demands matrices for each topology.
To closely mimic the real traffic, bandwidth of each BA demand is randomly chosen from the real demands matrices, but each scales down 5 $\times$ \cite{Teavar}.

%After a request arriving the system, we run admitted control algorithm to determine whether the request can be accommodated or not.
%As introduced above, $\mathsf{BATE}$ adopts Algorithm \ref{greedy} as its default option.
%We compare Algorithm \ref{greedy} (i.e, Greedy) with fixed algorithm and the optimal algorithm
%The fixed algorithm assumes all admitted requests are fixed and checks whether the remaining network capacity can support the new request.
%The optimal algorithm determines whether the new request can be admitted by solving (\ref{P8}). 
%Every time slot, we randomly generate an integer $p$ between 0 and 10000 for each link.
%If  $p/10000$ is smaller than the failure probability of the link, we make it down to emulate failure.
%Then after 5 time slots, we make the link up again.
%Each experiment lasts 200 time slots.
%The achieved availability of a service is computed as the percentage of qualified time slots, where a slot is regarded as qualified if the total bandwidth is not smaller than demand.
%The achieved availability can be derived by a post-processing simulation composed by network states.
%In each network state, we record the application level throughput ratio as well as the network state probability.
%The sum of network state probability in which the allocated bandwidth larger than the demand is regarded as the achieved availability.

Traffic engineering performs every 10 time slots.
For traffic engineering part, we compare the performance of $\mathsf{BATE}$ against FFC \cite{FFC}, TEAVAR \cite{Teavar}, SWAN \cite{swan}, SMORE \cite{SMORE}, B4 \cite{B4}.
We change them to adapt service level traffic engineering: 
FFC tries to maximize the link utilization with considering 1 fault could occur in our evaluation.
%To fairly compare the ability of the FFC algorithm, we let it
%send the entire demand at the expense of potential degradation in
%availability, unless otherwise stated
%TEAVAR uses the parameter $\beta$ to control the network service availability target
TEAVAR maximizes bandwidth allocation to each demand subject to a single operator-specified availability target.
The default availability target of TEAVAR is $99.9\%$ in our simulations.
SMORE \cite{SMORE} minimizes the maximum link utilization without explicit guarantees on availability.
SWAN \cite{swan}  tries to  maximize the total throughput of all demands in the current slot.
B4 \cite{B4} aims to deliver max-min fair allocation manner to each demand.
\fi

%We compare the failure recovery part with random rerouting mechanism when there are link failures. 
%However, SWAN 
%However, TEAVAR .
%SWAN 
%We can see that DC5 takes about 100ms to detect failure and DC1 hears it within 200ms.
%It takes about 200ms for the controller to derive the new traffic engineering results.
%Switches take about 500ms to update flow rules.
%DC4-DC5 link has large failure probability, so the scenario mentioned above is likely to happen.
%Traditionally,  SDN controller will take reactive interventions when there are failures.
%This will take too much time and QoS might have already been hurt disastrously. 
%This demonstrates that $\mathsf{BATE}$ considers failure scenarios \textit{proactively}.
%Services with large availability target will pass links with low risk probability. 
%Therefore, the availability target can be guaranteed.
%$\mathsf{BATE}$ considers the failure probability of links, thus, the availability demand of applications can be guaranteed.
%\begin{figure*}
%\centering
%\subfigure[Network state coverage]{
%\includegraphics[width=0.32\textwidth]{fig/coverage.pdf}}
%\subfigure[Error]{
%\includegraphics[width=0.32\textwidth]{fig/error.pdf}}
%\subfigure[Solution time]{
%\includegraphics[width=0.32\textwidth]{fig/optimizer_times.pdf}}
%\caption{Impact of pruning and accuracy of solution.}
%\label{purning_fig2}
%\end{figure*}
%As introduced above, $\mathsf{BATE}$ calls for application level volume between each DC pair.
%Our collected traffic data contains the capacity of all links and the  bandwidth demands between each DC pair.
%We don't have real bandwidth demands of each service.
%%We assume there are $|J|=30$ application flows in each DC pair.
%To conform real data center network traffic characters, we divide the original DC-pair bandwidth demands into $|J|$ parts randomly, where the default value of $J$ is 30.
%%Each part can be regarded as an application flow demand.
%Services call for diverse availability demands and we generate them with uniform distribution between 90\% and 99.99\%.  
%There are typically five importance levels in current data centers, i.e., significant,
%important, normal, unimportant and lax.
%We randomly assign weights to services within \{1,2,3,4,5\}with uniform distribution, which is similar to \cite{hanzhang}.
% $\mu(f_{jtk})=\sum_{k\in K, t \in T_k}f_{jtk}/d_j, \forall j \in J$ in our experiments.
%Default  profit is 1 when availability is achieved, otherwise, the profit is $\mu(R_j)=0.01\times R_j$.

@@

\textbf{Evaluation results.}
%From the comparison between the scheduled and testbed results, we can see that the scheduled results match the real testbed quite well,
%so in the following part, we will use trace-driven simulation to evaluate the performance of $\mathsf{BATE}$.
